Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2014-01-08 limits/ms.tex
Added a histogram showing the distribution of axis ratios across models.

\item Check that you and Claudio average to the same projected radius
  (one pixel past outermost image) when calculating
  $lambda_1/lambda_2$ and $\theta$.

@@

>>>>

\item \sout{Check that you and Claudio average to the same projected radius
  (one pixel past outermost image) when calculating
  $lambda_1/lambda_2$ and $\theta$.}. This is correct.

@@

\begin{figure}
\plotone{BCZContrastR1R3_TmS_shape.pdf}
\caption{}
\label{}
\end{figure}
